---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r}
#| echo: false
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```




# cranpackages: Check for CDC contributted R packages in CRAN


<!-- badges: start -->
[![R-CMD-check](https://github.com/CDCgov/cran-packages/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/CDCgov/cran-packages/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/CDCgov/cran-packages/graph/badge.svg)](https://app.codecov.io/gh/CDCgov/cran-packages)
<!-- badges: end -->


## Overview

Checks [CRAN](https://cran.r-project.org/) information for packages authored or
maintained by CDC employees, or those that declare CDC funding.
Looks in the undocumented file `packages.rds` as suggested by
[Jeroen Ooms](https://github.com/jeroen) in
in [this `stackoverflow` answer](https://stackoverflow.com/a/8830439).
While there is no guarantee that the file will continue to be available,
it exists _at least_ since Jan 2012, when that answer was provided.

Looks for `CDC`, `cdc.gov`, and `Disease Control` in the author and maintainer
fields for all packages listed in CRAN.
It does not look for archived packages.


## Usage

Unless you expect or know the file to have moved locations, the default `url`
should be fine.
Unless you want to try different search patterns, the default `regex` should be
fine.


This table was last updated on `r Sys.Date()`.

```{r eval=FALSE}
remotes::install_github("CDCgov/cran-packages")

library(package = "cranpackages")

get_cdc_authored()
```


```{r eval=TRUE, echo=FALSE, message=FALSE}
cdc_packages <- cranpackages::get_cdc_authored()

cdc_packages$Package <- paste0(
  "[", cdc_packages$Package, "](", cdc_packages$CRAN_URL, ")"
)

cdc_packages$CRAN_URL <- NULL

knitr::kable(cdc_packages)
```




```{r child=c("DISCLAIMER.md", "LICENSE.md")}

```
